\documentclass{exam}
\begin{document}
FINAL EXAM: CS3342b Tuesday, 25 April 2017, 2pm, Room FEB GYM\newline
\newline
\newline
\newline
NAME AS APPEARS ON STUDENT ID:\newline
\newline
STUDENT ID NUMBER:\newline
\newline
GAUL/CONFLUENCE USER NAME:\newline
\newline
REMINDERS:
\begin{enumerate}
\item (from course outline) The final exam will be closed book, closed notes, with no electronic devices allowed, with particular reference to any electronic devices that are capable of communication and/or storing information.
\item Write neatly.  If the marker can't read it, it is wrong.
\item This exam shouldn't take long to write.  On the other hand, time will pass.  It is a 3 hour exam with 50 questions.  If you complete a question every 3 minutes (or 10 questions every half hour), you will still have a half hour at the end to double check that everything is in order.
\item While you are not allowed to open the exam booklet until the proctor says you can, you can fill out the information on the cover page.  You should also get out your student id and make sure your pencils and pens are in order.  If you need to get something out of your jacket or knapsack once the exam has started, raise your hand and wait til a proctor comes to you to oversee the matter.
\end{enumerate}
\newpage
\begin{enumerate}
\item In Scala, the type that every type is a subtype of is called ANSWER.\newline
ANSWER=
\item In Haskell, we can declare the type of a parameter to a function to be something specific like Char.  However, we can also declare the type of a parameter to be something that could include many types like ListLike that supports the functions head and tail.  We do this with a definition of ListLike that begins with the keyword ANSWER.\newline
ANSWER=
\item In the Ruby community, the acronym DSL is an abbreviation for ANSWER.\newline
ANSWER=
\item ANSWER would be the derivation of ((1)) in the language defined by the context-free grammar consisting of the two rules $E \rightarrow ( E )$ and $E \rightarrow 1$.\newline
ANSWER=
\item In Ruby, by convention, the ? in the method me? is used to indicate that me is ANSWER.\newline
ANSWER=
\item In the ICD textbook's example interpreter for evaluating expressions, in the row labelled id, we have the code: v = lookup(vtable, getname(id)) ; if v = unbound then error() else v.  The value of v would be unbound in the situation that ANSWER.\newline
ANSWER=
\item Three concepts related to concurrency were discussed with regards to the language Io.  ANSWER was presented as a way to manage two execution streams that pass control back and forth between themselves.\newline
ANSWER=
\item The specific type of context-free grammar that was the main focus of the portion of the Syntax Analysis chapter that was assigned was ANSWER.\newline
ANSWER=
\item Unlike most Lisp systems, Clojure doesn't use its own custom virtual machine.  It was originally designed to compile to code that would run on the ANSWER.\newline
ANSWER=
\item Three concepts related to concurrency were discussed with regards to the language Io.  ANSWER was presented as a general mechanism for sending a message to an object that would cause that object to respond to the message as a separate process running asynchronously.\newline
ANSWER=
\item With respect to the value returned by the Ruby expression 'hi'.object\_id == 'hi'.object\_id, you can say it ANSWER.\newline
ANSWER=
\item In Ruby, if you declare a class with a class name that is already in use and put in it the definition of a new method, you have changed the functionality of the existing class (even if it is a predefined class like Fixnum).  The property of Ruby that allows this is ANSWER.\newline
ANSWER=
\item In the context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow B$, $A \rightarrow a$, $B \rightarrow b$, and $B \rightarrow$  the value of FIRST(A) is ANSWER.\newline
ANSWER=
\item If the types of a programming language are bound at execution time rather than compile time, then the types are called ANSWER.\newline
ANSWER=
\item A compiler typically keeps track of which names are associated with which objects by using ANSWER.\newline
ANSWER=
\item The root of the inheritance hierarchy in Ruby is the class ANSWER.\newline
ANSWER=
\item Programming languages that view programming as describing a step-by-step process to do something are called ANSWER languages.\newline
ANSWER=
\item Using the straightfoward statement translation scheme in the ICD textbook, if I were to TransStat('while z $<$ 3 do z := 1 + z', vtable, ftable), newvar() will be invoked ANSWER times.\newline
ANSWER=
\item In Haskell's do notation for working with monads, assignment uses the ANSWER operator.\newline
ANSWER=
\item The feature of programs being able to `write programs' (creating application specific language features) is called ANSWER.\newline
ANSWER=
\item The loop and recur constructs are in Clojure to guide ANSWER.\newline
ANSWER=
\item In Haskell, $\lbrack x * 2 | x \leftarrow \lbrack 3, 4, 5\rbrack \rbrack$  evaluates to ANSWER.\newline
ANSWER=
\item In Haskell, the type signature of the function sum x y = x + y is ANSWER.\newline
ANSWER=
\item One of the three most significant parts of a Haskell monad is called ANSWER, which unwraps a function.\newline
ANSWER=
\item The portion of the call stack associated with a single function invocation and execution is called ANSWER.\newline
ANSWER=
\item In Ruby, normally, when you try to add a String to a Fixnum, you get an error message saying that a String can't be coerced to a Fixnum.  This is because Ruby is ANSWER typed.\newline
ANSWER=
\item In Erlang, you can link two processes together.  Then when one dies, it sends ANSWER to its twin.\newline
ANSWER=
\item As one would expect in an object-oriented language, when a message is sent to an object, the first thing the system does is to look for a corresponding method in that object.  However, Io lets you change what happens next by redefining the method named ANSWER.\newline
ANSWER=
\item Instead of the +  symbol, Haskell uses the symbol ANSWER for a string concatenation operator.\newline
ANSWER=
\item When type checking done during program execution, the type system is called ANSWER.\newline
ANSWER=
\item In Prolog, the most natural way to express the query `what animals are cats?' is ANSWER.\newline
ANSWER=
\item Scala uses few type declarations because its compiler does ANSWER.\newline
ANSWER=
\item In Clojure, you cannot change a reference outside of ANSWER.\newline
ANSWER=
\item In Prolog, the expression $\lbrack 1, 2, 3\rbrack = \lbrack X | Y\rbrack$ causes Y to have the value ANSWER.\newline
ANSWER=
\item Io allows programmers to play with its syntax, doing things like introducing a colon operator and redefining how curly braces are processed.  This makes it easy to use Io to create ANSWER.\newline
ANSWER=
\item In Haskell, defining lists using a notation like $\lbrack x * 2 | x \leftarrow \lbrack 3, 4, 5\rbrack \rbrack$ is called using ANSWER.\newline
ANSWER=
\item In the ICD textbook's example interpreter for evaluating expressions, in the row labelled id, we have the code: v = lookup(vtable, getname(id)) ; if v = unbound then error() else v.  It says getname(id) instead of id, because ANSWER.\newline
ANSWER=
\item When a grammar can produce two distinct syntax trees for the same string, the grammar is said to be ANSWER.\newline
ANSWER=
\item In Io, the basic method for creating a new object is ANSWER.\newline
ANSWER=
\item One aspect of the if-then-else-end syntax of Ruby is that it avoids the ANSWER problem.\newline
ANSWER=
\item The Scala feature closest to a Ruby mixin is the ANSWER.\newline
ANSWER=
\item With respect to the value returned by the Ruby expression :hi.object\_id == :hi.object\_id, you can say it ANSWER.\newline
ANSWER=
\item In Haskell, ANSWER is the output of zip $\lbrack$17..20$\rbrack$ $\lbrack$10,8..4$\rbrack$.\newline
ANSWER=
\item Adding a feature to a programming language to make it easier to do something that was already doable is called adding ANSWER.\newline
ANSWER=
\item In Prolog, the expression $X = \lbrack \lbrack 1,2\rbrack | \lbrack 3,4\rbrack \rbrack$ causes X to have the value ANSWER.\newline
ANSWER=
\item When you write a parser for a context-free grammar that satisfies the LL(1) criteria by representing each non-terminal by a function that chooses what functions to invoke by the LL(1) criteria, this sort of parser is called ANSWER.\newline
ANSWER=
\item Some languages allow a function to be ANSWER, that is to be defined over a large class of similar types, e.g., over arrays no matter what type their elements are.\newline
ANSWER=
\item ANSWER means that the language allows the same name to be used for different operations over different types.\newline
ANSWER=
\item The specifications for how to group characters into meaningful units are traditionally written as ANSWER.\newline
ANSWER=
\item In Haskell, given the definition sum x y = x + y, ANSWER is the value of that is produced by the expression (sum 3).\newline
ANSWER=
\item Matz, the creator of Ruby, thinks that it is less important to optimize the execution (efficiency) of a programming language and more important to optimize the efficiency of ANSWER.\newline
ANSWER=
\item In a context-free grammar, the nonterminal that derives an entire member of the language being defined is called ANSWER.\newline
ANSWER=
\item In automatically generating the code that reads characters and outputs the part of a programming language that is analogous to its words, we start with a specification and then traditionally convert it into code in two stages.  In the first stage, we produce ANSWER.\newline
ANSWER=
\item Since a compiler may have to look up what object is associated with a name many times, it is typical to use ANSWER to avoid linear search times.\newline
ANSWER=
\item Many programming languages represent internal constants for types like strings, floats, and integers.  Scala has the unusual distinction of having an internal constant representation for the type ANSWER, which is normally viewed as a format external to a program.\newline
ANSWER=
\item In the chapter on Scala, we get the following interesting quote: ANSWER is the most important thing you can do to improve code design for concurrency.\newline
ANSWER=
\item Another method of parameter passing, whose technical name is ANSWER, is implemented by passing the address of the variable (or whatever the given parameter is).  Assigning to such a parameter would then change the value stored at the address.\newline
ANSWER=
\item In Prolog, the most natural way to express the rule that `I am an ancestor of you if I am a parent of you' is ANSWER.\newline
ANSWER=
\item In Clojure, ANSWER is a concurrency construct that allows an asynchronous return before computation is complete.\newline
ANSWER=
\item A major claim in object-oriented design philosophy is that you should code to ANSWER rather than code to the implementation.\newline
ANSWER=
\item In Haskell, if I write (h:t) = $\lbrack$3, 5, 7$\rbrack$, ANSWER is the value of h.\newline
ANSWER=
\item The command name for the Ruby interpreter is ANSWER.\newline
ANSWER=
\item When type checking done during program compilation, the type system is called ANSWER.\newline
ANSWER=
\item Since Haskell doesn't have traditional error handling mechanisms, by convention, people use the ANSWER monad to distinguish a valid return from an error return.\newline
ANSWER=
\item In C, when you pass a function as a parameter to another function, it is implemented as passing ANSWER.\newline
ANSWER=
\item In Io, we create a singleton by redefining the method ANSWER.\newline
ANSWER=
\item One of the three most significant parts of a monad is called ANSWER, which wraps up a function and puts it in the monad's container.\newline
ANSWER=
\item In Prolog, the expression hi(X, 4) = hi(3, Y) causes X to have the value ANSWER.\newline
ANSWER=
\item In the context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow B$, $A \rightarrow a$, $B \rightarrow b$, and $B \rightarrow$  the value of Nullable(A) is ANSWER.\newline
ANSWER=
\item The technical term for the compiler design methodology where the translation closely follows the syntax of the language is ANSWER.\newline
ANSWER=
\item Using the context-free grammar based on the two rules $A \rightarrow b A$ and $A \rightarrow b$, ANSWER would be the derivation sequence for bbb.\newline
ANSWER=
\item To execute a code block in Ruby that is passed to a method on its parameter list, you send that parameter the method ANSWER.\newline
ANSWER=
\item ANSWER is the data structure used in language translation to track the binding of variables and functions to their type.\newline
ANSWER=
\item In Io, the type of an object is generally the nearest ancestor that ANSWER.\newline
ANSWER=
\item The different traversals of a syntax tree done during compilation associate information with the nodes of the tree.  The technical term for this kind of information is ANSWER.\newline
ANSWER=
\item One approach to speeding up an interpreter is to translate pieces of the code being interpreted directly into machine code during program execution, this is called ANSWER.\newline
ANSWER=
\item In Haskell, instead of defining second by writing something like second x = head( tail(  x ) ), you can write this without introducing the parameter x by using function composition.  Doing that, you would define second by ANSWER.\newline
ANSWER=
\item If the system stack is used for a call stack, then it becomes important for the caller to update the top of the stack before copying items into it.  The reason is because we are worried about the top of the stack being changed by ANSWER after we have copied in information but before we updated the stack top.\newline
ANSWER=
\item To execute a code block in Ruby that is passed to a method but doesn't appear on its parameter list, you use the keyword ANSWER.\newline
ANSWER=
\item ANSWER is the regular expression that corresponds to the language defined by the context-free grammar with the three rules $A \rightarrow A a$, $A \rightarrow A b$, $A \rightarrow a$.\newline
ANSWER=
\item Although Haskell is a statically typed language, we usually don't need to write type declarations because Haskell uses ANSWER to figure out what the types are.\newline
ANSWER=
\item The central idea of context-free grammars is to define a language by productions.  These productions say that a nonterminal symbol can be replaced by ANSWER.\newline
ANSWER=
\item In Scala, the type that is a subtype of every type is called ANSWER.\newline
ANSWER=
\item The main Clojure approach to concurrency is called ANSWER.\newline
ANSWER=
\item In Ruby, you would group methods into a class.  In Erlang, you group functions into ANSWER.\newline
ANSWER=
\item The : notation in the Ruby expressions :hi is used to indicate that hi is ANSWER.\newline
ANSWER=
\item When the structure of the syntax tree is used to determine which object corresponds to a name, this is called ANSWER.\newline
ANSWER=
\item In Erlang, the main approach to concurrency is ANSWER.\newline
ANSWER=
\item In Clojure, the value of (repeat 1) is ANSWER.\newline
ANSWER=
\item ANSWER data structures have the property that there are operations on the structure that can destroy or modify it.\newline
ANSWER=
\item In Ruby, the expression Fixnum.class returns ANSWER.\newline
ANSWER=
\item In discussing object-oriented languages, objects are organized into a class tree to support the property of ANSWER.\newline
ANSWER=
\item In discussing object-oriented languages, being able to handle objects of related types is called ANSWER.\newline
ANSWER=
\item In Ruby, true.class returns ANSWER.\newline
ANSWER=
\item In the ICD textbook's example interpreter for evaluating expressions, in the row labelled let id = Exp1 in Exp2, we have the code: v1 = EvalExp(Exp1, vtable, ftable); vtableP = bind(vtable, getname(id), v1), EvalExp(Exp2, vtableP, ftable).  The bind function changes vtable into vtableP by ANSWER.\newline
ANSWER=
\item In Io, a message has three aspects that can be interrogated by the call method.  They are: the sender, the reciever, and ANSWER.\newline
ANSWER=
\item When you define a method in a class, normally it is meant to be invoked on an object of that class (an instance method).  Sometimes it is meant to be invoked on the class name itself (a class method), like Date.parse('3rd Feb 2001').  In Ruby, to define a class method, we put ANSWER at the beginning of the method name in its definition.\newline
ANSWER=
\item Scala was designed to connect two programming paradigms, which were ANSWER.\newline
ANSWER=
\item The way Haskell handles functions with more than one parameter is called ANSWER.\newline
ANSWER=
\item In Ruby, the @@ is used to indicate that the variable @@me is ANSWER.\newline
ANSWER=
\item The application that caused a significant increase in the popularity of Ruby was a web framework called ANSWER.\newline
ANSWER=
\item The specifications of how to group characters into meaningful basic units of a programming language are generally implemented in code that has the abstract form of ANSWER.\newline
ANSWER=
\item Many syntax features of Erlang, such as ending statements with a period, reflect the influence of the programming language ANSWER.\newline
ANSWER=
\item ANSWER are two derivations of the string cc that produce distinct syntax trees from the context-free grammar $X \rightarrow X c Y$ , $Y \rightarrow X$ ,  $Y \rightarrow$ and $X \rightarrow$ .\newline
ANSWER=
\item ANSWER data structures have the property that no operation on the structure will destroy or modify it.\newline
ANSWER=
\item In Scala, if I want to redefine a method that is defined in my parent class, I indicate this by using the keyword ANSWER.\newline
ANSWER=
\item The portion of the program where the name is visible is called its ANSWER.\newline
ANSWER=
\item When viewed formally, a language is defined as a set of ANSWER.\newline
ANSWER=
\item In the ICD textbook's example interpreter for evaluating expressions, in the row labelled id(Exps), we have the code: args = EvalExps(Exps,vtable,ftable).  We pass ftable to EvalExps to handle ANSWER.\newline
ANSWER=
\item In Ruby, the name of the method in the class Me that is automatically invoked when a new object of type Me is created with Me.new is ANSWER.\newline
ANSWER=
\item In Clojure, (take 3 (iterate (fn $\lbrack$x$\rbrack$ (* 2 x)) 2)) produces ANSWER.\newline
ANSWER=
\item In Scala, to indicate that a variable is mutable, you introduce it with the ANSWER keyword.\newline
ANSWER=
\item In Prolog, the expression 2 = 1 + X causes X to have the value ANSWER.\newline
ANSWER=
\item In describing the properties of an object-oriented language, encapsulation means ANSWER.\newline
ANSWER=
\item In Haskell, if we want to define a local named function inside a function definition, we use the keyword ANSWER.\newline
ANSWER=
\item An unusual built-in constant construct in Erlang lets us write $<<4:3,1:3>>$ to represent the value ANSWER.\newline
ANSWER=
\item In Prolog, the most natural way to express the rule that `I am an ancestor of you if I am a parent of an ancestor of you' is ANSWER.\newline
ANSWER=
\item Using the straightfoward statement translation scheme in the ICD textbook, if I were to TransStat('while true do z := 1 + z', vtable, ftable), newlabel() will be invoked ANSWER times.\newline
ANSWER=
\item The main concurrency approach used in Ruby is ANSWER.\newline
ANSWER=
\item If I wanted to fix the grammar $E \rightarrow E + E$ and $E \rightarrow id$, so that it would only produce one syntax tree, which is left recursive; the new grammar would be ANSWER.\newline
ANSWER=
\item In the context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow a$, $B \rightarrow b$, $B \rightarrow$  the value of Nullable(A) is ANSWER.\newline
ANSWER=
\item Io is known for taking ANSWER -based approach to object-oriented programming.\newline
ANSWER=
\item The main programming paradigm in Erlang is ANSWER programming.\newline
ANSWER=
\item When viewing programming languages as natural languages, the word ANSWER is used instead of `words'.\newline
ANSWER=
\item In the ICD textbook's example interpreter for evaluating expressions, in the row labelled id(Exps), we have the code: args = EvalExps(Exps,vtable,ftable).  We pass vtable to EvalExps to handle ANSWER.\newline
ANSWER=
\item The \& notation in the line of Ruby def george(\&sam) is used to indicate that sam is ANSWER.\newline
ANSWER=
\item In most languages, a function definition like f a b = a : (f (a + b) b) would result in an infinite recursion.  However, in Haskell we can partially evaluate functions like this because Haskell is based on ANSWER.\newline
ANSWER=
\item Using the straightfoward expression translation scheme in the ICD textbook, if I were to TransExp('3 * x + 1', vtable, ftable), newvar() will be invoked ANSWER times.\newline
ANSWER=
\item In Prolog, the most natural way to express the fact that `a lion is a cat' is ANSWER.\newline
ANSWER=
\item In Haskell, instead of writing something like if x == 0 then 1 else fact ( x - 1 ) * x, you can write a series of lines starting with $|$ x $>$ 1 = x * factorial ( x - a).  This second style is called ANSWER.\newline
ANSWER=
\item In Haskell, ANSWER is the output of zip $\lbrack$20..17\rbrack$ $\lbrack$10,8..4\rbrack$.\newline
ANSWER=
\item In the context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow a$, $B \rightarrow b$, $B \rightarrow$  the value of FOLLOW(A) is ANSWER.\newline
ANSWER=
\item In the context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow a$, $B \rightarrow b$, $B \rightarrow$  the value of FIRST(A) is ANSWER.\newline
ANSWER=
\item In Prolog, the expression $\lbrack 1, 2, 3\rbrack = \lbrack X | Y\rbrack$ causes X to have the value ANSWER.\newline
ANSWER=
\item The routine in a compiler that takes as input a sequence of characters outputs these characters grouped into meaningful units is called ANSWER.\newline
ANSWER=
\item Ruby supports two common ways that boolean expressions are handled in programming languages.  In one approach, both subexpressions of a boolean operator are evaluated before the boolean operator is evaluated.  In the other approach, called ANSWER, the first subexpression in a boolean expression is evaluated and, if that is enough to know the result of the boolean expression, then the second subexpression is not evaluated.\newline
ANSWER=
\item Programming languages that view programming as describing characteristics of the problem domain and characteristics of the solution and leaving it to the language processor to find a solution are called ANSWER languages.\newline
ANSWER=
\item In Haskell, instead of writing something like if x == 0 then 1 else fact ( x - 1 ) * x, you can write a series of lines starting with factorial 0 = 1.  This second style is called ANSWER.\newline
ANSWER=
\item In Haskell, you use the keyword ANSWER to collect related code into a similar scope.\newline
ANSWER=
\item The type of a string constant in Haskell, by default, is written ANSWER.\newline
ANSWER=
\item In Prolog, the expression that would cause an unbound variable X to take on the sum of the values of a bound variable Y and a bound variable Z is ANSWER.\newline
ANSWER=
\item The context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow a$, $B \rightarrow b$, $B \rightarrow$  is not LL(1) specifically because ANSWER.\newline
ANSWER=
\item The ! in Scala is used to ANSWER.\newline
ANSWER=
\item In Ruby, the mixin is used to solve the object-oriented programming problem of ANSWER.\newline
ANSWER=
\item When a function is invoked, if the language passes a copy of the value of each parameter to the code that performs the function, this is called ANSWER.\newline
ANSWER=
\item A code block in Ruby is some lines of code surrounded by either curly braces or ANSWER.\newline
ANSWER=
\item In the context-free grammar $A \rightarrow B A$ , $B \rightarrow A B$, $A \rightarrow B$, $A \rightarrow a$, $B \rightarrow b$, and $B \rightarrow$  the value of FOLLOW(A) is ANSWER.\newline
ANSWER=
\item Another design goal for Scala was to have its programs easily interoperate with those written in ANSWER.\newline
ANSWER=
\item The Greek letter epsilon, when talking about languages, is used to represent ANSWER.\newline
ANSWER=
\item One way of checking types is to see what constructor was used to create an object that is a parameter.  Another way of checking types is to wait until a method is sent to an object and see if it supports the method.  This second way is called ANSWER\newline
ANSWER=
\item In Prolog, the expression hi(X, 4) = hi(3, X) causes X to have the value ANSWER.\newline
ANSWER=
\item The idea that when a process has an error, it is up to a monitoring process to determine what to do about the problem is referred to by the motto ANSWER in Erlang.\newline
ANSWER=
\item In Prolog, the expression X = 1 + 2 causes X to have the value ANSWER.\newline
ANSWER=
\item The main programming paradigm for Clojure is ANSWER programming.\newline
ANSWER=
\item In Ruby, the evaluation of arguments to a message are handled by the object sending the message.  In Haskell, the runtime environment decides when and how much to evaluate an argument to a function.  In Io, the evaluation of the arguments to a message is made by ANSWER.\newline
ANSWER=
\item The technical term for connecting a name with an object is ANSWER.\newline
ANSWER=
\item In the Erlang community, ANSWER code refers to replacing pieces of your application without stopping your application.\newline
ANSWER=
\item In Ruby, if a line starts with a method name, that method is being sent to the object named ANSWER.\newline
ANSWER=
\item Using the straightfoward statement translation scheme in the ICD textbook, if I were to TransStat('if true then z := 1 else z := 2', vtable, ftable), newlabel() will be invoked ANSWER times.\newline
ANSWER=
\item In Scala, to indicate that a variable is immutable, you introduce it with the ANSWER keyword.\newline
ANSWER=
\item In Haskell, the anonymous function ANSWER causes the expression `map ANSWER $\lbrack 1, 2, 3\rbrack$' to produce $\lbrack -4, -5, -6\rbrack$.\newline
ANSWER=
\item Three concepts related to concurrency were discussed with regards to the language Io.  ANSWER was presented as a way to request that something be computed and then be able to continue computing until the result was needed.  If the result was available, then things would proceed as expected.  If the result was not available, then a wait would be initiated until the result became available.\newline
ANSWER=
\item ANSWER typing is when the language implementation ensures that the arguments of an operation are of the type the operation is defined for.\newline
ANSWER=
\item The main concurrency method used in Scala is ANSWER.\newline
ANSWER=
\item When you send a message to a Ruby object, Ruby first looks at the methods that object supports, and then starts working the inheritance chain.  If it still can't find the appropriate method, the message and its parameters get passed as a message to the original object looking for a method called ANSWER.\newline
ANSWER=
\item Scala is ANSWER typed\newline
ANSWER=
\item In Ruby, the @ is used to indicate that the variable @me is ANSWER.\newline
ANSWER=
\item In Haskell, if I define a function double x = x + x, its type signature would be ANSWER.\newline
ANSWER=
\item A programming language is called ANSWER, if it is executed directly by an interpreter rather than by first being compiled with a compiler.\newline
ANSWER=
\item In Haskell, if I write (h:t) = $\lbrack$3, 5, 7$\rbrack$, ANSWER is the value of t.\newline
ANSWER=
\item Each named object will have ANSWER, where the name is defined as a synonym for the object.\newline
ANSWER=
\item In automatically generating the code that reads characters and outputs the part of a programming language that is analogous to its words, we start with a specification and then traditionally convert it into code in two stages.  The main problem that can arise in moving from the first stage to the second stage is ANSWER.\newline
ANSWER=
\item In Prolog, the expression hi(X, 4) = hi(3, Y) causes Y to have the value ANSWER.\newline
ANSWER=
\end{enumerate}
\newpage
\begin{verbatim}
exam_database_file= examdatabase.json
exam_format= latex
dump_database= false
line_width= 72
question_count= 173
create_exam= false
answer_key= true
sample_seed= 222
shuffle_seed= 2345
["ICD1", "ICD2", "ICD3", "ICD4", "ICD5", "ICD6", "ICD9", "SLSW2",
"SLSW3", "SLSW4", "SLSW5", "SLSW6", "SLSW7", "SLSW8"]
["ICD1", "ICD2", "ICD3", "ICD4", "ICD5", "ICD6", "ICD9", "SLSW2",
"SLSW3", "SLSW4", "SLSW5", "SLSW6", "SLSW7", "SLSW8"]
\end{verbatim}
\begin{enumerate}
\item Any
\item class
\item domain specific language
\item $E \Rightarrow (E) \Rightarrow ((E)) \Rightarrow ((1))$
\item boolean
\item \begin{itemize}
\item getname(id) was not declared
\item getname(id) was not bound
\end{itemize}
\item coroutines
\item LL(1)
\item \begin{itemize}
\item JVM
\item Java Virtual Machine
\end{itemize}
\item Actors
\item could be either true or false
\item open classes
\item $\{a,b\}$
\item dynamically typed
\item \begin{itemize}
\item a symbol table
\item an environment
\end{itemize}
\item Object
\item imperative
\item 5
\item $\leftarrow$
\item metaprogramming
\item \begin{itemize}
\item tail recursion optimization
\item tail recursion elimination
\end{itemize}
\item $\lbrack 6, 8, 10\rbrack$
\item $(Num \quad a) => a \rightarrow a \rightarrow a$
\item \begin{itemize}
\item $>>=$
\item a bind function
\end{itemize}
\item an activation record
\item strongly
\item an exit signal
\item forward
\item ++
\item dynamic typing
\item \begin{itemize}
\item animal(What), cat(What).
\item animals(What), cats(What).
\item is\_a(What, animal), is\_a(What, cat).
\item are(What, animals), are(What, cats).
\end{itemize}
\item type inferencing
\item a transaction
\item $\lbrack 2, 3\rbrack$
\item \begin{itemize}
\item Domain Specific Languages
\item DSLs
\end{itemize}
\item list comprehensions
\item id indicates a token with a type and value field
\item ambiguous
\item clone
\item dangling else
\item trait
\item will always be true
\item $\lbrack$(17,10),(18,8),(19,6),(20,4)$\rbrack$
\item syntactic sugar
\item $\lbrack \lbrack 1, 2\rbrack, 3, 4\rbrack$
\item a recursive descent parser
\item \begin{itemize}
\item polymorphic
\item generic
\end{itemize}
\item Overloading
\item regular expressions
\item $(\setminus x \rightarrow 3 + x)$
\item the programmers
\item a start symbol
\item \begin{itemize}
\item a nondeterministic finite automata
\item a nondeterministic finite state machine
\end{itemize}
\item hash tables
\item XML
\item Immutability
\item \begin{itemize}
\item call-by-reference
\item pass-by-reference
\end{itemize}
\item ancestor(I, You) :- parent(I, You).
\item a future
\item interface
\item 3
\item irb
\item static typing
\item Maybe
\item the address of the start of the function code
\item clone
\item return
\item 3
\item true
\item syntax-directed translation
\item $A \Rightarrow Ab \Rightarrow Abb \Rightarrow bbb$
\item call
\item A symbol table
\item \begin{itemize}
\item has a name that starts with a capital letter
\item has a slot for the method type
\end{itemize}
\item attributes
\item just-in-time compilation
\item second = head . tail
\item an interrupt
\item yield
\item $a (a|b)*$
\item type inference
\item \begin{itemize}
\item a sequence of terminals and nonterminals
\item a sequence of symbols
\end{itemize}
\item Nothing
\item \begin{itemize}
\item Software Transactional Memory
\item STM
\end{itemize}
\item a module
\item a symbol
\item \begin{itemize}
\item static scoping
\item lexical scoping
\end{itemize}
\item actors
\item \begin{itemize}
\item an infinite sequence of 1s
\item a lazy infinite sequence of 1s
\end{itemize}
\item \begin{itemize}
\item imperative
\item destructively updated
\item mutable
\end{itemize}
\item Class
\item inheritance
\item polymorphism
\item TrueClass
\item \begin{itemize}
\item inserting the association of getname(id) with the value v1 into the table
\item inserting the binding of getname(id) with the value v1 into the table
\end{itemize}
\item the argument list
\item self.
\item object-oriented and functional
\item currying
\item a class variable
\item \begin{itemize}
\item Rails
\item Ruby on Rails
\end{itemize}
\item \begin{itemize}
\item a finite automata
\item a finite state machine
\end{itemize}
\item Prolog
\item $X \Rightarrow XcY \Rightarrow XcYcY \Rightarrow cYcY \Rightarrow ccY \Rightarrow cc$ AND $X \Rightarrow XcY \Rightarrow XcX \Rightarrow XcXcY \Rightarrow cXcY \Rightarrow ccY \Rightarrow cc$
\item \begin{itemize}
\item persistent
\item functional
\item immutable
\end{itemize}
\item override
\item scope
\item strings
\item expressions that contain function usages
\item initialize
\item (4 8 16)
\item var
\item \begin{itemize}
\item X remains unbound
\item X remains unbound and the expression fails
\end{itemize}
\item \begin{itemize}
\item data and behavior are packaged together
\item there is a mechanism for restricting access to an object's components
\end{itemize}
\item where
\item \begin{itemize}
\item !
\item octal 41
\item decimal 33
\item hexidecimal 21
\end{itemize}
\item ancestor(I, You) :- parent(I, Ancestor), ancestor(Ancestor, You). 
\item 3
\item threads
\item \begin{itemize}
\item $E \rightarrow E + F$ and $E \rightarrow F$ and $F \rightarrow id$
\item $E \rightarrow E + F$ and $E \rightarrow id$ and $F \rightarrow id$
\end{itemize}
\item false
\item a prototype
\item functional
\item tokens
\item expressions that contain identifiers
\item a code block
\item lazy evaluation
\item 5
\item \begin{itemize}
\item cat(lion).
\item is\_a(lion, cat).
\end{itemize}
\item using guards
\item $\lbrack\rbrack$
\item $\{b\}$
\item $\{a,b\}$
\item 1
\item \begin{itemize}
\item a lexical analyzer
\item a scanner
\item a lexer
\end{itemize}
\item short-circuit evaluation
\item declarative
\item pattern matching
\item module
\item $\lbrack$Char$\rbrack$
\item X is Y + Z
\item FIRST(BA) and FIRST(a) both include a, so we do not know which A rule to use
\item send a message to an actor
\item multiple inheritance
\item \begin{itemize}
\item call-by-value
\item pass-by-value
\end{itemize}
\item do end
\item $\{a,b\}$
\item Java
\item the empty string
\item duck typing
\item \begin{itemize}
\item X will not be bound and the expression will fail
\item X will not be bound
\end{itemize}
\item Let It Crash
\item 1+2
\item functional
\item the reciever of the message
\item binding
\item hot-swapping
\item self
\item 3
\item val
\item $(\setminus x \rightarrow - (x + 3))$
\item Futures
\item Strong
\item actors
\item method\_missing
\item statically
\item an instance variable
\item $(Num \quad a) \Rightarrow a \rightarrow a$
\item interpreted
\item $\lbrack$5, 7$\rbrack$
\item a declaration
\item an exponential explosion in the number of states needed
\item 4
\end{enumerate}
\end{document}
